---
title: "Data Science day 1"
author: "Wajid Umar"
date: "07/10/2021"
output: html_document
---

This is our first day of data science course.
My name is Wajid Umar and I am learning data science.

Basic ploting

1-simple plot
```{r}
x<-iris
plot(x$Sepal.Length,x$Sepal.Width, xlab = "sepal length", ylab = "sepal width", main = "scatter")
```

Relational plot
```{r}
plot(x)
```

2-histogram
```{r}
hist(x$Petal.Length)
```

3-boxplot
```{r}
boxplot(x$Sepal.Length~x$Species, data = x)
```

4-image graph
```{r}
y<-matrix(1:120, 12,10)
y
image(y)
```

5-strip chart
```{r}
stripchart(x$Sepal.Length)
```

6-qqnorm plot
```{r}
qqnorm(x$Petal.Length)
```

Intermediate plot

7 scatter plot

first of all we need to calculate corelation
```{r}
library(corrplot)
v<-cor(iris[1:4])
corrplot(v)
```

another diverse data set
```{r}
c<-cor(mtcars)
corrplot(c)
```

in number formate
```{r}
corrplot(c, method = "number")
```

upper corr plot
```{r}
corrplot(c, method = "number", type = "upper")
```

lower corrplot
```{r}
corrplot(c, method = "number", type = "lower")
```

mixed corrplot
```{r}
corrplot.mixed(c, lower = "number", upper = "pie", order="AOE")
```

clustering
```{r}
corrplot(c, order = "hclust", addrect = 2)
```

Another method to make correlation plot

```{r}
library(PerformanceAnalytics)
chart.Correlation(c, histogram = TRUE, method = "pearson")

```










